---
title: "Grouping Canberra suburbs (gammaX[location])"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r echo = FALSE,	message = FALSE,	warning = FALSE}
## Global options
# options(max.print="75")
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache = FALSE,
	cache.path = "docs/",
	# width=75,
	comment = NA,
	prompt = FALSE,
	tidy = TRUE
)

#and suburbs
# devtools::install_github("wfmackey/absmapsdata")
#stat zones from SA3
library(tidyverse)
library(absmapsdata)
# dat <- read.csv("")
##current dataset.. 
#import now
# library(tidyverse)
library(ggmap)
library(leaflet)
library(plotly)
library(flexdashboard)
library(DT)
library(rgdal)
library(crosstalk)
# library(absmapsdata)
library(sf)

```

Overall we can group locations and other attributes into different spatial areas. For mapping many projects the exact location is not know or is not needed/wanted for a range of obvious reasons. This set of functions takes the location information from each of the datasets and creates a uniform location entry that aligns with the desired spatial scale.

```{r}
library(mapview)
library(leafpop)

pnt <- data.frame(x = 174.764474, y = -36.877245)
pnt <- st_as_sf(pnt, coords = c("x", "y"), crs = 4326)
img <- "https://upload.wikimedia.org/wikipedia/commons/thumb/6/62/Mount_Eden.jpg/640px-Mount_Eden.jpg"

mapview(pnt, map.types = "Esri.WorldImagery",
        popup = popupImage(img, src = "remote"))
# ??popupImage

mapview(pnt, popup = leafpop:::popupIframe("https://www.youtube.com/embed/iApz08Bh53w?autoplay=1", width = 300, height = 225))
```

## Final selection figure

```{r}
allfiles <- list.files("../data/allfiles/August/", pattern=c("table_", ".csv"), full.names = TRUE)

countsperupdate <- function(allfiles){
  
  allfiledat <- list() #<- list() MUST BE OUTSIDE

    for(i in 1:length(allfiles)) {
      tib <- read_csv(allfiles[i]) %>%
            dplyr::select(Contact, Date, Suburb, Status) #%>%
              # filter(Status == "New" & Suburb == "Dickson")
      
    allfiledat[[i]] <- as.data.frame(tib)
  } #end loop
  
  return(allfiledat)
  
} #end function

##setup list of data
allfiledat <- list()

#run function
allfiledat <- countsperupdate(allfiles = allfiles)

# ??addCircleMarkers
##how to do this???
# for(i in 1:length(allfiledat)){
  # i=1
 # singledatpostcode <- allfiledat[[10]] %>%
 #  left_join(postcodesACT1, by = c('Suburb')) %>%
 #  remove_missing() 
 # i = 2
 # singledat <- allfiledat[[20]] %>%
 #  # left_join(postcodesACT1, by = c('Suburb')) %>%
 #  remove_missing() 
 
 # row_bind
 
# }
##plot the map
m <- leaflet() %>% addTiles()
m
# #only fours match up :)
# m1 <- m %>%
#   addCircleMarkers(lat=singledatpostcode$latitude,
#                    lng=singledatpostcode$longitude)
# 
# m1
```

This constitutes one of the challenges that is unique to a small collection of areas which are small and surrounded by much larger states and districts.

```{r eval = FALSE}
cols <- c( "red", "yellow","blue")
datRaw$Contact <- factor(datRaw$Contact,levels=c(  "Close"  , "Casual", "Monitor") )
  cc <- as.numeric( datRaw$Contact)
  ncols <- c("black","cyan")
  nn <- as.numeric(factor(datRaw$Status))
  nn2 <- ifelse(nn==1,nn, 3)
  
  # glimpse(datRaw)
  
  datRaw$Date <- substr(datRaw$Date,1,10) #ditch day of the week
  labs <- paste(datRaw$Contact, datRaw$Status,datRaw$Exposure.Location, datRaw$Street, datRaw$Suburb, datRaw$Date,datRaw$Arrival.Time, datRaw$Departure.Time, datRaw$doubles, sep="<br/>") 

  dataJoin <- absmapsdata::sa12016 %>%
    filter(gcc_name_2016 == "Australian Capital Territory") %>%
    mutate(Suburb = sa2_name_2016) %>%
    left_join(datRaw, by = c("Suburb")) %>%
    select(Suburb, lat, lon, Exposure.Location, geometry,Status, Contact) %>%
    na.omit() %>%
    mutate(Status = ifelse(Status == "New", "New", "Previous")) %>%
    st_as_sf
  
  glimpse(dataJoin)cols <- c( "red", "yellow","blue")

  datRaw$Contact <- factor(datRaw$Contact,levels=c(  "Close"  , "Casual", "Monitor") )
  cc <- as.numeric( datRaw$Contact)
  ncols <- c("black","cyan")
  nn <- as.numeric(factor(datRaw$Status))
  nn2 <- ifelse(nn==1,nn, 3)
  
  # glimpse(datRaw)
  
  datRaw$Date <- substr(datRaw$Date,1,10) #ditch day of the week
  labs <- paste(datRaw$Contact, datRaw$Status,datRaw$Exposure.Location, datRaw$Street, datRaw$Suburb, datRaw$Date,datRaw$Arrival.Time, datRaw$Departure.Time, datRaw$doubles, sep="<br/>") 

  dataJoin <- absmapsdata::sa12016 %>%
    filter(gcc_name_2016 == "Australian Capital Territory") %>%
    mutate(Suburb = sa2_name_2016) %>%
    left_join(datRaw, by = c("Suburb")) %>%
    select(Suburb, lat, lon, Exposure.Location, geometry,Status, Contact) %>%
    na.omit() %>%
    mutate(Status = ifelse(Status == "New", "New", "Previous")) %>%
    st_as_sf
  
  glimpse(dataJoin)
```

### Levels of possible grouping {.tabset .tabpills}

The raw data has the following location variables of interest:

```{r}
############very ugly function But should work.....

#dataList is a list...
##ARD sep2021
# last_five_days_new <- function(dataList){

  # <NA> and NA
  # 
  # # remove_missing(vars = c("Exposure.Location"))%>%  # let's just look Melbourne
  # plot1 <-  ggplot(dataJoin,aes(y=lat, x=lon)) +
  #   ggspatial::annotation_map_tile() +
  #   geom_sf(aes(geometry = geometry, fill = Status), 
  #           col = c("red"), 
  #           lty = 1, alpha =0.5)+ 
  #   scale_fill_manual(values = c("red", "yellow","blue")) + 
  #   geom_point(data = dataJoin, aes(y=lat, x=lon), size = 4, alpha = 0.3) #+ 
  # scale_fill_manual(values = c("red", "yellow","blue","black", "white")) +
  # scale_color_manual(values = c("red", "yellow","blue","black", "white")) 
  
  # return(plot1)  
  
# }  #function end


#lapply
# p1 <- last_five_days_new(dataList = "./data/allfiles/September/table_01_Sep_2021_136pm.csv")


# dataList = "./data/allfiles/September/table_01_Sep_2021_136pm.csv"
# lapply(dataList, last_five_days_new)

# p1



```

#### Unique set of points

```{r}
#census data
#postcode data
# open source map data
    #no new sites test
# dataList = "./data/allfiles/September/table_01_Sep_2021_136pm.csv"
dataList = "../data/last.csv"
tab3 <- read.csv(dataList)
# glimpse(tab3)

#the uncleaned data is what we have to work with
#here it is September 2021

datRaw <- read.csv("../data/allfiles/September/table_01_Sep_2021_136pm.csv")
glimpse(datRaw)

```


#### Manual grouping into four general areas.... {.tabset .tabpills}

Here I have created for groups: North Canberra, Central Canberra,.....

```{r}
# e.g
subsNorth <- c("Watson", "Hackett")
subsEast <- c("Bruce")
subsCentral <- c("Canberra")
subsSouth <- c("Woden")
outsideACTregion <- c("Jervis Bay", "Wreck Bay", "Hmas Creswell", "Coree", "Mount Stromlo", "Uriarra")

#     for(i in 1:length(allfiles)) {
#       tib <- read_csv(allfiles[i]) %>%
#             dplyr::select(Contact, Date, Suburb, Status) %>%
#               filter(Status == "New")
#       
#     allfiledat[[i]] <- as.data.frame(tib)
#   } #end loop
# 
# postcodesACT1 <- postcodesACT %>%
#                   mutate(Suburb = place_name)
# 
# singledatpostcode <- allfiledat[[1]] %>%
#   left_join(postcodesACT1, by = c('Suburb'))
# 
# 
# m1 <- m %>%
#   addCircleMarkers(lat=singledatpostcode$latitude,
#                    lng=singledatpostcode$longitude) +
#   addPolygons(datArea1)
# 
# m1
```


#### Suburb

This is the grouping variable for location provided by the ACT website. This information is helpful but needs to be filtered to check that every Suburb matches a Postcode?

```{r}

```


#### Postcode

There are xx postcodes in the ACT. we can associate each one of these with a suburb?

```{r}
# absmapsdata::postcode2016
#downloaded csv
postcodesACT <- read.csv("../data/au_postcodes.csv") %>%
  dplyr::filter(state_name == "Australian Capital Territory")

# str(postcodesACT$place_name)

outsideACTregion <- c("Jervis Bay", "Wreck Bay", "Hmas Creswell", "Coree", "Mount Stromlo", "Uriarra")

postcodesACT1 <- postcodesACT %>%
                  mutate(Suburb = place_name)
# glimpse(postcodesACT)

#standard baseline
# ggmap()

p1 <- ggplot(postcodesACT1) +
  geom_point(aes(y = latitude, x = longitude)) +
  geom_text(aes(y = latitude, x = longitude, label=place_name),hjust=10, vjust=10) + 
  geom_abline(intercept = (max(postcodesACT1$latitude)- min(postcodesACT1$latitude))/2 + min(postcodesACT1$latitude), slope = 0) + 
  geom_vline(xintercept = (max(postcodesACT1$longitude)- min(postcodesACT1$longitude))/2 + min(postcodesACT1$longitude), linetype="dotted", 
                color = "blue", size=1.5) + 
  theme_minimal()
  # geom_line(aes(x = (max(postcodesACT$longitude)- min(postcodesACT$longitude))/2 + min(postcodesACT$longitude), y = 0)
  # geom_label(aes(y = latitude, x = longitude))

mw <- plotly::ggplotly(p1)

mw
```

#### ACT Census data

```{r}
# load library
library(OpenStreetMap)
# extract map
AustraliaMap <- openmap(c(-8,110),
    c(-45,160),
#   type = "osm",
#   type = "esri",
    type = "nps",
    minNumTiles=7)
# plot map
plot(AustraliaMap)
```

*From ABS package*

```{r}
# sa32016 
map <- lga2018 %>%
  filter(state_name_2016 == "Australian Capital Territory") %>%   # let's just look Melbourne
  ggplot() +
  geom_sf(aes(geometry = geometry,  # use the geometry variable
              fill = areasqkm_2018),     # fill by area size
          lwd = 0,                  # remove borders
          show.legend = FALSE) +    # remove legend
  geom_point(aes(cent_long,
                 cent_lat),        # use the centroid long (x) and lats (y)
             colour = "white") +    # make the points white
  theme_void() +                    # clears other plot elements
  coord_sf()

map
```

```{r}
DT::datatable(lga2018 %>%
  filter(state_name_2016 == "Australian Capital Territory"))
```

This package allows aspects of this data to be linked with census and other data resources associated with this level of geo-spatial identification.

#### LGA_2016 equates to total of ACT

```{r}
library(sf)
library(raster)
library(dplyr)
library(spData)
library(spDataLarge)

dat <- as.data.frame(absmapsdata::lga2016)

seine_simp = st_simplify(absmapsdata::lga2016, dTolerance = 2000) 
plot(seine_simp)


#removes 3 postcoides in NSW jervis area
datArea <- as.data.frame(absmapsdata::lga2016) %>%
          dplyr::select(state_name_2016, lga_name_2016,areasqkm_2016) %>%
            dplyr::filter(!state_name_2016 %in% outsideACTregion)


datArea <- absmapsdata::lga2016 %>%
          # dplyr::select(state_name_2016, lga_name_2016,areasqkm_2016) %>%
            dplyr::filter(!lga_name_2016 %in% outsideACTregion)

datArea1 <- datArea  %>%
          # dplyr::select(state_name_2016, lga_name_2016,areasqkm_2016) %>%
            dplyr::filter(state_name_2016 == 'Australian Capital Territory')

ACTwide <- datArea1[1,]
# plot(ACTwide)

seine_simp = st_simplify(ACTwide, dTolerance = 2000) 
# plot(seine_simp)


# str(dat)
# table(dat$lga_name_2016)

dat2 <- datArea %>%
  dplyr::filter(state_name_2016 == "Australian Capital Territory")

DT::datatable(dat2)

ACTlga <- dat[558, ]

#ACT multipoly
ACTpoly <- ACTlga$geometry[[1]]

ACTpolyGG <- 
ACTpoly %>%
fortify() 

# ACTpolyGG
# %>%
# mutate(aux = c("1"))

# ACTpolyGG$geometry[[1]]
# 
# %>%
# fortify()  %>%
# mutate(aux = c("1"))
# 
# ggplot() +
# geom_polygon(data = ACTpolyGG)
# 
# 
# sf_transform_xy(ACTpoly)
```

```{r echo = FALSE, eval = FALSE}
# attr(,"class")
# [1] "XY"           "MULTIPOLYGON" "sfg" 
# ggspatial::geom_spatial_polygon(ACTlga)
library(plotly)
library(ggplotlyExtra)
library(leaflet)

allfiles <- list.files("../data/allfiles/August/", pattern=c("table_", ".csv"), full.names = TRUE)
#sort patterns

length(allfiles)
allfiles <- allfiles[51]

##sort wrong files


countsperupdate <- function(allfiles){

  allfiledat <- list() #<- list() MUST BE OUTSIDE

    for(i in 1:length(allfiles)) {
      tib <- read_csv(allfiles[i]) %>%
            dplyr::select(Contact, Date, Suburb, Status) %>%
              filter(Status == "New")

    allfiledat[[i]] <- as.data.frame(tib)
  } #end loop

  return(allfiledat, w)

} #end function
# 
# ##setup list of data
allfiledat <- list()
# 
# #run function
allfiledat <- countsperupdate(allfiles = allfiles)

# shape_areas <- shape_df %>%
#   st_as_sf(coords = c("lon", "lat")) %>%
#   group_by(var) %>%
#   summarise(do_union = F) %>%
#   st_cast("POLYGON") %>%
#   st_cast("MULTIPOLYGON") %>%
#   mutate(area = st_area(geometry)) %>% 
#   mutate(var = as.factor(var)) 

##plot the map
m <- leaflet() %>% addTiles()

# head(ACTlga$geometry)
# m %>%
  # addPolygons(ACTlga[[]])
```

LGA_2016 equates to total of ACT

```{r}
dat <- as.data.frame(absmapsdata::lga2016)

#removes 3 postcoides in NSW jervis area
datArea <- as.data.frame(absmapsdata::lga2016) %>%
          dplyr::select(state_name_2016, lga_name_2016,areasqkm_2016) %>%
            dplyr::filter(!state_name_2016 %in% outsideACTregion)

# str(dat)
# table(dat$lga_name_2016)

dat2 <- datArea %>%
  dplyr::filter(state_name_2016 == "Australian Capital Territory")

DT::datatable(dat2)

ACTlga <- dat[558, ]

#ACT multipoly
ACTpoly <- ACTlga$geometry[[1]]

ACTpolyGG <- 
ACTpoly %>%
fortify() 

# ACTpolyGG
# %>%
# mutate(aux = c("1"))

# ACTpolyGG$geometry[[1]]
# 
# %>%
# fortify()  %>%
# mutate(aux = c("1"))
# 
# ggplot() +
# geom_polygon(data = ACTpolyGG)
# 
# 
# sf_transform_xy(ACTpoly)
```

```{r echo = FALSE, eval = FALSE}
# attr(,"class")
# [1] "XY"           "MULTIPOLYGON" "sfg" 
# ggspatial::geom_spatial_polygon(ACTlga)
library(plotly)
library(ggplotlyExtra)
library(leaflet)

allfiles <- list.files("../data/allfiles/August/", pattern=c("table_", ".csv"), full.names = TRUE)
#sort patterns

length(allfiles)
allfiles <- allfiles[51]

##sort wrong files


countsperupdate <- function(allfiles){

  allfiledat <- list() #<- list() MUST BE OUTSIDE

    for(i in 1:length(allfiles)) {
      tib <- read_csv(allfiles[i]) %>%
            dplyr::select(Contact, Date, Suburb, Status) %>%
              filter(Status == "New")

    allfiledat[[i]] <- as.data.frame(tib)
  } #end loop

  return(allfiledat, w)

} #end function
# 
# ##setup list of data
allfiledat <- list()
# 
# #run function
allfiledat <- countsperupdate(allfiles = allfiles)

# shape_areas <- shape_df %>%
#   st_as_sf(coords = c("lon", "lat")) %>%
#   group_by(var) %>%
#   summarise(do_union = F) %>%
#   st_cast("POLYGON") %>%
#   st_cast("MULTIPOLYGON") %>%
#   mutate(area = st_area(geometry)) %>% 
#   mutate(var = as.factor(var)) 

##plot the map
m <- leaflet() %>% addTiles()

# head(ACTlga$geometry)
# m %>%
  # addPolygons(ACTlga[[]])
```

All current locations in cases

```{r fig.align="c"}
# absmapsdata::postcode2016
#downloaded csv
postcodesACT <- read.csv("../data/au_postcodes.csv") %>%
  dplyr::filter(state_name == "Australian Capital Territory")

# str(postcodesACT$place_name)

postcodesACT1 <- postcodesACT %>%
            dplyr::filter(!place_name %in% outsideACTregion)
# glimpse(postcodesACT)

#standard baseline
# ggmap()

p1 <- ggplot(postcodesACT1) +
  geom_point(aes(y = latitude, x = longitude)) +
  geom_text(aes(y = latitude, x = longitude, label=place_name),hjust=10, vjust=10) + 
  geom_abline(intercept = (max(postcodesACT1$latitude)- min(postcodesACT1$latitude))/2 + min(postcodesACT1$latitude), slope = 0) + 
  geom_vline(xintercept = (max(postcodesACT1$longitude)- min(postcodesACT1$longitude))/2 + min(postcodesACT1$longitude), linetype="dotted", 
                color = "blue", size=0.9, alpha = 0.7) + 
  theme_minimal()
  # geom_line(aes(x = (max(postcodesACT$longitude)- min(postcodesACT$longitude))/2 + min(postcodesACT$longitude), y = 0)
  # geom_label(aes(y = latitude, x = longitude))

mw <- plotly::ggplotly(p1)

mw
            # plotly::add_annotations(p =mw, text = postcodesACT$place_name)

```

#### SA3 statistical Areas

```{r}
# sa32016
map <- sa32016 %>%
  filter(gcc_name_2016 == "Australian Capital Territory") %>%   # let's just look Melbourne
  ggplot() +
  geom_sf(aes(geometry = geometry)) +   # use the geometry variable
  geom_point(aes(cent_long, cent_lat))  # use the centroid long (x) and lats (y)

map
```

#### SA2 statistical Areas

```{r}
DT::datatable(sa22016 %>%
  filter(gcc_name_2016 == "Australian Capital Territory"))

```

```{r}
# sa32016
library(plotly)
map <- sa22016 %>%
  filter(gcc_name_2016 == "Australian Capital Territory") %>%   # let's just look Melbourne
  ggplot() +   
  ggspatial::annotation_map_tile(zoom = 8) +
  geom_sf(aes(geometry = geometry, fill  = areasqkm_2016)) #   # use the geometry variable
  # geom_point(aes(cent_long, cent_lat))  # use the centroid long (x) and lats (y)
map


# ggplotly(map)
```

Overall we can group locations and other attributes into different spatial areas. Here I have created for groups: North Canberra, Central Canberra,...Manual grouping into four general areas....

```{r}
# e.g
subsNorth <- c("Watson", "Hackett")
subsEast <- c("Bruce")
subsCentral <- c("Canberra")
subsSouth <- c("Woden")
outsideACTregion <- c("Jervis Bay", "Wreck Bay", "Hmas Creswell", "Coree", "Mount Stromlo", "Uriarra")
```

This package allows aspects of this data to be linked with census and other data resources associated with this level of geo-spatial identification.

```{r eval = TRUE}
library(plotly)
library(maps)
library(leaflet)
# ??addC
##plot the map
m <- leaflet() %>% addTiles()

# absmapsdata::postcode2016
#downloaded csv
# absmapsdata::postcode2016
#downloaded csv
postcodesACT <- read.csv("../data/au_postcodes.csv") %>%
                  mutate(Suburb = place_name) %>%
  dplyr::filter(state_name == "Australian Capital Territory")

# str(postcodesACT$place_name)

outsideACTregion <- c("Jervis Bay", "Wreck Bay", "Hmas Creswell", "Coree", "Mount Stromlo", "Uriarra")

postcodesACT1 <- postcodesACT %>%
            dplyr::filter(!Suburb %in% outsideACTregion)

m1 <- m %>%
  addCircleMarkers(lat=postcodesACT1$latitude,
                   lng=postcodesACT1$longitude)

m1
```

#### SA1 statistical Areas

```{r}
DT::datatable(sa12016 %>%
  filter(gcc_name_2016 == "Australian Capital Territory"))

map <- sa12016 %>%
  filter(gcc_name_2016 == "Australian Capital Territory") %>%   # let's just look Melbourne
  ggplot() +
  geom_sf(aes(geometry = geometry)) +   # use the geometry variable
  geom_point(aes(cent_long, cent_lat))  # use the centroid long (x) and lats (y)

map
```

