---
title: "Breaking down suburbs into counts"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

Locations are reported on the ACT Health site including 

```{r echo = FALSE, message = FALSE, warning=FALSE}
library(tidyverse)
library(leaflet)
cities <- read.csv(textConnection("
City,Lat,Long,Pop
Boston,42.3601,-71.0589,645966
Hartford,41.7627,-72.6743,125017
New York City,40.7127,-74.0059,8406000
Philadelphia,39.9500,-75.1667,1553000
Pittsburgh,40.4397,-79.9764,305841
Providence,41.8236,-71.4222,177994
"))

leaflet(cities) %>% addTiles() %>%
  addCircles(lng = ~Long, lat = ~Lat, weight = 1,
    radius = ~sqrt(Pop) * 30, popup = ~City
  )
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

```{r}
library(lubridate)
library(tidyverse)

tab3 <- read_csv("https://raw.githubusercontent.com/green-striped-gecko/covid_canberra/main/data/last.csv")

str(tab3)

# names(tab3)
datyl <-factor(tab3$Contact)
# levels(datyl)

datyl1 <- tab3 %>%
           filter(Status >= "New")

names(tab3)
# colsN <- cols[datyl1]

tab4 <- tab3 %>%
  mutate(colsN = factor(Contact, levels = c("Close", "Casual", "Monitor","Investigation location")),
         Contact = factor(Contact, levels = c("Close", "Casual","Monitor", "Investigation location")))


levels(tab4$colsN) <- c("purple", "red","orange",  "grey50")
levels(tab4$colsN) <- c( "yellow", "red","cyan", "blue")
table(tab4$colsN)

names(tab4)
tab4 %>%
  mutate(conDate = as.Date(lubridate::dmy(Date)),
         locName = as.factor(Exposure.Location))


##loc summaries
tab5 <- tab4 %>%
  mutate(conDate = as.Date(lubridate::dmy(Date)),
         locName = as.factor(Suburb)) 

a <- as.data.frame(table(tab5$locName))

colnames(a) <- c("locName", "contactcount")

# head(a)
# str(a)
# filter(a, contactcount >=1)

plotsumms <- right_join(tab5, a)

print(a)
str(a)

# Aggregate method
# labs <- paste(plotsumms$Exposure.Location, plotsumms$Date,plotsumms$Arrival.Time, plotsumms$Departure.Time, sep="<br/>") 

nrow(tab4)
#> [1] 100
nrow(distinct(plotsumms, Suburb))
b <- distinct(plotsumms, Suburb, .keep_all = TRUE)
# subsTable <- semi_join(tab4, b)


#> [1] 69
# nrow(distinct(df, x, y))
# #> [1] 69
levels(plotsumms$locName)
# distinct(df, x)
plotsumms <- b
plotsumms$Suburb[35] <- "O'Connor" 
plotsumms$locName[35] <- "O'Connor"
# plotsumms$Suburb <- droplevels(plotsumms$Suburb)
# plotsumms$locName <- droplevels(plotsumms$locName)

clean <- plotsumms$Exposure.Location[4] <- "Assembly The People Pub"

# pre-processing
# ensure that all characters in the `Name` column
# are valid UTF-8 encoded
# Thank you to SO for this gem 
# https://stackoverflow.com/questions/17291287/how-to-identify-delete-non-utf-8-characters-in-r
Encoding(x = plotsumms$Exposure.Location) <- "UTF-8"

# replace all non UTF-8 character strings with an empty space
plotsumms$Exposure.Location <-
  iconv( x = plotsumms$Exposure.Location
         , from = "UTF-8"
         , to = "UTF-8"
         , sub = "" )


labs <- paste(plotsumms$Exposure.Location, plotsumms$Date,plotsumms$Arrival.Time, plotsumms$Departure.Time, sep="<br/>") 

leaflet(plotsumms) %>% addTiles() %>%
  addCircleMarkers(lat=plotsumms$lat,
                            lng=plotsumms$lon,
                   weight = 0.2, 
    radius = log(plotsumms$contactcount)*5, 
                            color = plotsumms$colsN,
                            stroke = TRUE,
                            fill = rep("black", length(plotsumms$colsN)),
                            popup = paste0(" COUNT:", plotsumms$contactcount),
                            fillOpacity = 0.8
                            ) %>%
  addCircles(lat=tab4$lat,lng=tab4$lon,
             popup = paste0(plotsumms$Exposure.Location," ", plotsumms$Date))

# %>%
#     group_by(locName) %>%
#       summarise(countPlace = count(Place))
# # %>%
#   group_by(Suburb) %>%
#     summarise(FirstCase = min(conDate),
#               LastCase = max(conDate),
#               caseCount = sum(unique(Place)))

# write.csv(x = plotsumms, "data/outSubs.csv")
```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
