---
title: "Timeline"
author: "Anthony Davidson"
output:
  html_document:
    df_print: paged
---

# Sorting out times and datas

This is a nasty task in any project however it is important to understand how much data we have and how that might be changing as we are developing and publishing the results. To check this we can recreate the date folder and run a set of functions over this until we get a useable variable.

```{r  echo = FALSE, message = FALSE, warning = FALSE}
library(here)
library(tidyverse)

# require(devtools)
# install_github("Displayr/flipTime")
library(flipTime)
##as.Dat
# seq(as.Date("2004-01-31"), by = "month", length = 10) e
##around
flipTime::AsDateTime("9/10/2010 10:20PM")
```

# Summarised outcome {.tabset}

This report captures a Exposure.location and suburb. The location information needs to be added to this. We have done that in another process and this work takes the following variables and converts the outcome into a visualiable set of location variables:

```{r}
dat <- read.csv("../data/last.csv")

glimpse(dat)
# dat$Date <- as.Date(lubridate::dmy(dat$Date))
dat$caseS <- dat$Arrival.Time
dat$caseE <- dat$Departure.Time

# ampm <- ifelse(dat$caseS == str_detect("am"), dat$caseAM, dat$casePM)
# 30/08/2021 - Monday
# library(tidyverse)
# # mutate(dat, 
#        dat$Dayall = str_split(dat$Date, " - ", n = 2)
#        for(i in 1:length(dat$Dayall)){
#          dat$DayDate[i] <-  dat$Dayall[[i]][2]
#          dat$dateCase[i] <-  dat$Dayall[[i]][1]
#        }
#        
#        
       dat$dateonly <- as.Date(lubridate::dmy(dat$Date))
#        
    dat$datetimeS <- flipTime::AsDateTime(paste0(dat$dateonly," ", dat$Arrival.Time))
       
      dat$datetimeE <- flipTime::AsDateTime(paste0(dat$dateonly," ", dat$Departure.Time))
              
              glimpse(dat)
      # select time levedata()
      
  datTimeSumms <-   dat %>%
        select(dateonly, datetimeS, datetimeE, Suburb, Status, Contact, lat, lon) %>%
    mutate(monthF = lubridate::month(dateonly),
           weekF = lubridate::week(dateonly), 
           dayF = lubridate::day(dateonly),
           daysteps = paste0(weekF, dayF))
 
  
  ggplot(datTimeSumms, aes(x= dateonly, y= Contact))+
        geom_jitter(aes(fill=Contact, group = daysteps),height = 0, width=0.01)+
    geom_smooth() + 
  xlab("update #")+
  ylab("# exposure sites")+
  # facet_wrap(~weekF) + 
  ggtitle("Exposure sites over updates since 16th August 2021")
  
  # ?geom_bar
  
    ggplot(datTimeSumms, aes(x= dateonly, y= Contact))+
        geom_jitter(aes(fill=Contact, group = daysteps),height = 0, width=0.01)+
    geom_smooth() + 
  xlab("update #")+
  ylab("# exposure sites")+
  # facet_wrap(~Contact) + 
  ggtitle("Exposure sites over updates since 16th August 2021")
  
      ggplot(datTimeSumms, aes(x= dateonly, y= Contact))+
        geom_jitter(aes(fill=Contact, group = daysteps),height = 0.1, width=0.1)+
    geom_smooth() + 
  xlab("update #")+
  ylab("# exposure sites")+
  # facet_wrap(~weekF) + 
  ggtitle("Exposure sites over updates since 16th August 2021")
      
      
            ggplot(datTimeSumms, aes(x= dateonly, y= Contact))+
        geom_jitter(aes(fill=Contact, group = daysteps),height = 0.2, width=0.5)+
    geom_smooth(aes(fill=Contact, group = Contact)) + 
  xlab("update #")+
  ylab("# exposure sites")+
  # facet_wrap(~weekF) + 
  ggtitle("Exposure sites over updates since 16th August 2021")
            
            
            
                 ggplot(datTimeSumms, aes(x= dateonly, group= Contact))+
        # geom_jitter(aes(fill=Contact, group = daysteps),height = 0.2, width=0.5)+
                   geom_density(aes(group = Contact,fill=Contact)) + 
    # geom_smooth() + 
  xlab("update #")+
  ylab("# exposure sites")+
  # facet_wrap(~weekF) + 
  ggtitle("Exposure sites over updates since 16th August 2021")
            
                
                 
                      ggplot(datTimeSumms, aes(x = dateonly, group = Contact))+
        # geom_jitter(aes(fill=Contact, group = daysteps),height = 0.2, width=0.5)+
                   geom_density(aes(group = Contact, fill = Contact), alpha = 0.3)+ 
    # geom_smooth() + 
  xlab("update #")+
  ylab("Density exposure sites")+
  facet_wrap(~weekF) + 
  ggtitle("Density of updates since 16th August 2021")                  
                      
                      # datDY <- dygraphs::

                        
library(dygraphs)
library(xts)          # To make the convertion data-frame / xts format
library(tidyverse)
library(lubridate)
 
# Read the data (hosted on the gallery website)
# data <- read.table("https://python-graph-gallery.com/wp-content/uploads/bike.csv", header=T, sep=",") %>% head(300)

# Check type of variable

 datTimeSumms1 <- datTimeSumms %>%
   group_by(Contact, dateonly) %>%
   tally() %>%
   ungroup(.)
 
 
ggplot(datTimeSumms1, aes(x=dateonly,y=n, group = Contact))+
  geom_bar(stat="identity", position = "stack", width=1, aes(fill=Contact))+
  xlab("update #")+
  ylab("# exposure sites")+
  ggtitle("`New` Exposure sites over updates")

ggplot(datTimeSumms1, aes(x=dateonly,y=n, group = Contact))+
  geom_point(aes(fill=Contact))+
  xlab("update #")+
  ylab("# exposure sites")+
  ggtitle("`New` Exposure sites over updates")

```

- Exposure.location
- Suburb
- Date


```{r}
#  datTimeSumms1$dateonly
#  
# # Since my time is currently a factor, I have to convert it to a date-time format!
# datTimeSumms1$dateonly <- ymd_hms(datTimeSumms1$dateonly)
# 
# 
#  # Then you can create the xts necessary to use dygraph
#   don <- xts(x = datTimeSumms1$datetime, order.by = datTimeSumms1$datetime, factor(datTimeSumms1$Contact))
# ?xts
#   
# Then you can create the xts necessary to use dygraph
  don <- xts(x = datTimeSumms1$n, order.by = datTimeSumms1$dateonly, factor(datTimeSumms1$Contact))
  
?xts
  
  
# Finally the plot
p <- dygraph(don, group = datTimeSumms1$Contact) %>%
  dyOptions(labelsUTC = TRUE, fillGraph=TRUE, fillAlpha=0.1, drawGrid = FALSE, colors="#D8AE5A") %>%
  dyRangeSelector() %>%
  dyCrosshair(direction = "vertical") %>%
  dyHighlight(highlightCircleSize = 5, highlightSeriesBackgroundAlpha = 0.2, hideOnMouseOut = FALSE)  %>%
  dyRoller(rollPeriod = 1)

p
# save the widget
# library(htmlwidgets)
# saveWidget(p, file=paste0( getwd(), "/HtmlWidget/dygraphs318.html"))
# Examples
# data(sample_matrix)
# sample.xts <- as.xts(sample_matrix, descr='my new xts object')
# 
# class(sample.xts)
# str(sample.xts)
# 
# head(sample.xts)  # attribute 'descr' hidden from view
# attr(sample.xts,'descr')
# 
# sample.xts['2007']  # all of 2007
# sample.xts['2007-03/']  # March 2007 to the end of the data set
# sample.xts['2007-03/2007']  # March 2007 to the end of 2007
# sample.xts['/'] # the whole data set
# sample.xts['/2007'] # the beginning of the data through 2007
# sample.xts['2007-01-03'] # just the 3rd of January 2007

x <- xts(matrix(1:(9*6),nc=6),
         order.by=as.Date(13000,origin="1970-01-01")+1:9,
         a1='my attribute')

xtsAttributes(x)
xtsAttributes(x) <- list(a2=2020)

xtsAttributes(x)
xtsAttributes(x) <- list(a1=NULL)
xtsAttributes(x)
```

#### COntact time lengths

```{r}
timingList <- data.frame(dat$caseS, dat$caseE)
# write.csv(timingList, "../data/testTIMS.csv")

# , dat$caseS -dat$caseE)
```

```{r eval = FALSE}
#########function 1 ####################
fileFiles_function <- function(filesiwant){
  allfiles <- list.files(filesiwant, pattern=c("table_", ".csv"), full.names = TRUE)
  return(allfiles)
}
# Exposure sites per Update for august amd sept
filesiwant <- c("./data/allfiles/August/", "../data/allfiles/September/")

allfiles <- suppressWarnings(fileFiles_function(filesiwant = filesiwant))
res <- data.frame(update=NA, date=NA,locations=NA, contact=NA,nsites=NA )
cc<-1         

for(i in 1:length(allfiles)){
  
  dd <- allfiledat[[i]]         
  tt <- table(dd$Contact)
  
  if (length(tt)>0) {
  for (ii in 1:length(tt))
    {
    res[cc, 1] <- i
    res[cc,2] <- (substr(dd$Date[i], 1,10))
    res[cc,3] <- nrow(dd)
    res[cc,4] <- names(tt)[ii]
    res[cc,5] <- tt[ii]
    cc <- cc+1
    }
  }
}
  

res <- res[!res$contact=="Investigation information",]
res <- res[!res$contact=="Investigation location",]
res$contact <- factor(res$contact, levels=c("Close", "Casual","Monitor"))


res <- res[order(res$contact),]
cols <- c( "red", "yellow","blue")[as.numeric(res$contact)]

ggplot(res, aes(x=update,y=nsites))+geom_bar(stat="identity", position = "stack", width=1, aes(fill=contact))+
  xlab("update #")+
  ylab("# exposure sites")+
  ggtitle("`New` Exposure sites over updates")
```

## Looks like?

Data stored as list of csvs in rds file called raw_rds

```{r  echo = FALSE, message = FALSE, warning = FALSE}
#########function 1 ####################
fileFiles_function <- function(filesiwant){
  allfiles <- list.files(filesiwant, pattern=c("table_", ".csv"), full.names = TRUE)
  return(allfiles)
}
# Exposure sites per Update for august amd sept
filesiwant <- c("./data/allfiles/August/", "../data/allfiles/September/")

allfiles <- suppressWarnings(fileFiles_function(filesiwant = filesiwant))



############function 2 ######################
##function to link all files into a list[[i]]
countsperupdate <- function(allfiles){
  
  allfiledat <- list() #<- list() MUST BE OUTSIDE

    for(i in 1:length(allfiles)) {
      tib <- read_csv(allfiles[i]) %>%
            dplyr::select(Contact, Date, Suburb, Status) #%>%
              #filter(Status == "New" & Suburb == "Gungahlin")
      
    allfiledat[[i]] <- as.data.frame(tib)
  } #end loop
  
  return(allfiledat)
  
} #end function

##setup list of data
allfiledat <- list()
#run function
allfiledat <- suppressWarnings(countsperupdate(allfiles = allfiles))
```





#### Basic points

```{r}
#csvs generated from
# £these need checking
# source("R/resAugustScript.R")
# and
# source("R/resSeptemberscript.R")

#new entries rather than accumulation of cases held by ACT
resA <- read.csv('../data/resAugust.csv')
resS <- read.csv('../data/resSeptember.csv')

resS<- resS %>%
  mutate(update = max(resA$update)+ update)

res <- bind_rows(resA, resS)

ggplot(res, aes(x=update,y=nsites))+
  geom_bar(stat="identity", position = "stack", width=1, aes(fill=contact))+
  xlab("update #")+
  ylab("# exposure sites")+
  ggtitle("`New` Exposure sites over updates")

ggplot(res,aes(x=update,y=nsites, group = contact,fill=contact, col = contact))+
  geom_point(size=4)+
  geom_line()+
  xlab("update #")+
  ylab("# exposure sites")+
  ggtitle("`New` Exposure sites over updates")
```













<!-- ## "New" Exposure sites per update (since outbreak) -->

<!-- ```{r echo = FALSE, message = FALSE, warning = FALSE} -->
<!-- #csvs generated from -->
<!-- # source("R/resAugustScript.R") -->
<!-- # and -->
<!-- # source("R/resSeptemberscript.R") -->

<!-- #new entries rather than accumulation of cases held by ACT -->
<!-- resA <- read.csv('../data/resAugust.csv') -->
<!-- resS <- read.csv('../data/resSeptember.csv') -->

<!-- resS<- resS %>% -->
<!--   mutate(update = max(resA$update )+ update) -->

<!-- res <- bind_rows(resA, resS) -->

<!-- ggplot(res, aes(x=update,y=nsites))+geom_bar(stat="identity", position = "stack", width=1, aes(fill=contact))+ -->
<!--   xlab("update #")+ -->
<!--   ylab("# exposure sites")+ -->
<!--   ggtitle("`New` Exposure sites over updates") -->
<!-- ``` -->

<!-- ## September -->

<!-- ```{r echo = FALSE, message = FALSE, warning = FALSE} -->
<!-- # Exposure sites per Update -->
<!-- allfiles <- list.files("../data/allfiles/September/", pattern=c("table_", ".csv"), full.names = TRUE) -->

<!-- # allfilesA <- list.files("../data/allfiles/August/", pattern=c("table_", ".csv"), full.names = TRUE) -->


<!-- countsperupdate <- function(allfiles){ -->

<!--   allfiledat <- list() #<- list() MUST BE OUTSIDE -->

<!--     for(i in 1:length(allfiles)) { -->
<!--       tib <- read_csv(allfiles[i]) %>% -->
<!--             dplyr::select(Contact, Date, Suburb, Status) %>% -->
<!--               filter(Status == "New") -->
<!--       #add status = new or previous -->

<!--     allfiledat[[i]] <- as.data.frame(tib) -->
<!--   } #end loop -->

<!--   return(allfiledat) -->

<!-- } #end function -->

<!-- ##setup list of data -->
<!-- allfiledat <- list() -->

<!-- #run function -->
<!-- allfiledat <- countsperupdate(allfiles = allfiles) -->

<!-- res <- data.frame(update=NA, date=NA,locations=NA, contact=NA,nsites=NA ) -->
<!-- cc<-1          -->

<!-- for(i in 1:length(allfiles)){ -->

<!--   dd <- allfiledat[[i]]          -->
<!--   tt <- table(dd$Contact) -->

<!--   if (length(tt)>0) { -->
<!--   for (ii in 1:length(tt)) -->
<!--     { -->
<!--     res[cc, 1] <- i -->
<!--     res[cc,2] <- (substr(dd$Date[i], 1,10)) -->
<!--     res[cc,3] <- nrow(dd) -->
<!--     res[cc,4] <- names(tt)[ii] -->
<!--     res[cc,5] <- tt[ii] -->
<!--     cc <- cc+1 -->
<!--     } -->
<!--   } -->
<!-- } -->



<!-- res <- res[!res$contact=="Investigation information",] -->
<!-- res <- res[!res$contact=="Investigation location",] -->
<!-- res$contact <- factor(res$contact, levels=c("Close", "Casual","Monitor")) -->


<!-- res <- res[order(res$contact),] -->
<!-- cols <- c( "red", "yellow","blue")[as.numeric(res$contact)] -->

<!-- ggplot(res, aes(x=update,y=nsites))+geom_bar(stat="identity", position = "stack", width=1, aes(fill=contact))+xlab("update #")+ylab("# exposure sites")+ggtitle("Exposure sites over updates") -->

<!-- ``` -->

<!-- ## Days in outbreak and contact counts (only new entries) -->

<!-- Hot days in current dataset (only new entries)?  -->

<!-- This information is for visual understanding only and may not represent the true risk or prevalence in the community or areas defined below. -->

<!-- We can take a dynamic snapshot of the hot spots by taking this curated dataset and running the following analysis: -->

<!-- ```{r eval = TRUE , message = FALSE, warning = FALSE} -->
<!-- ############function 2 ###################### -->
<!-- ##function to link all files into a list[[i]] -->
<!-- countsperupdate <- function(allfiles){ -->

<!--   allfiledat <- list() #<- list() MUST BE OUTSIDE -->

<!--     for(i in 1:length(allfiles)) { -->
<!--       tib <- read_csv(allfiles[i]) %>% -->
<!--             dplyr::select(Contact, Date, Suburb, Status) #%>% -->
<!--               # filter(Status == "New") -->

<!--     allfiledat[[i]] <- as.data.frame(tib) -->
<!--   } #end loop -->

<!--   return(allfiledat) -->

<!-- } #end function -->

<!-- ##setup list of data -->
<!-- allfiledat <- list() -->
<!-- #run function -->
<!-- allfiledat <- countsperupdate(allfiles = allfiles) -->

<!-- #write this as  -->
<!-- for(i in 1:length(allfiles)){ -->

<!--   dd <- allfiledat[[i]]          -->
<!--   tt <- table(dd$Contact) -->

<!--   if (length(tt)>10) { -->
<!--   for (ii in 1:length(tt)) -->
<!--     { -->
<!--     res[cc, 1] <- i -->
<!--     res[cc,2] <- (substr(dd$Date[i], 1,10)) -->
<!--     res[cc,3] <- nrow(dd) -->
<!--     res[cc,4] <- names(tt)[ii] -->
<!--     res[cc,5] <- tt[ii] -->
<!--     cc <- cc+1 -->
<!--     } -->
<!--   } -->
<!-- } -->

<!-- glimpse(allfiledat) -->
<!-- # allfiledat -->

<!-- res1 <- filter(res,  nsites > 10) -->

<!-- res1 <- res1[!res1$contact=="Investigation information",] -->
<!-- res1 <- res1[!res1$contact=="Investigation location",] -->
<!-- res1$contact <- factor(res1$contact, levels=c("Close", "Casual","Monitor")) -->


<!-- res1 <- res1[order(res1$contact),] -->
<!-- cols <- c( "red", "yellow","blue")[as.numeric(res1$contact)] -->

<!-- ggplot(res1, aes(x=date,y=nsites))+geom_bar(stat="identity", position = "stack", width=1, aes(fill=contact))+ -->
<!--   xlab("update #")+ -->
<!--   ylab("# exposure sites")+ -->
<!--   ggtitle("Hotspots days (based on contact day)") -->

<!-- ``` -->

<!-- ## "New" Exposure sites for September (Dickson) -->

<!-- ```{r echo = FALSE, message = FALSE, warning = FALSE} -->
<!-- # Exposure sites per Update for august -->
<!-- allfiles <- list.files("../data/allfiles/September/", pattern=c("table_", ".csv"), full.names = TRUE) -->

<!-- countsperupdate <- function(allfiles){ -->

<!--   allfiledat <- list() #<- list() MUST BE OUTSIDE -->

<!--     for(i in 1:length(allfiles)) { -->
<!--       tib <- read_csv(allfiles[i]) %>% -->
<!--             dplyr::select(Contact, Date, Suburb, Status) %>% -->
<!--               filter(Status == "New" & Suburb == "Dickson") -->

<!--     allfiledat[[i]] <- as.data.frame(tib) -->
<!--   } #end loop -->

<!--   return(allfiledat) -->

<!-- } #end function -->

<!-- ##setup list of data -->
<!-- allfiledat <- list() -->

<!-- #run function -->
<!-- allfiledat <- countsperupdate(allfiles = allfiles) -->

<!-- res <- data.frame(update=NA, date=NA,locations=NA, contact=NA,nsites=NA ) -->
<!-- cc<-1          -->

<!-- for(i in 1:length(allfiles)){ -->

<!--   dd <- allfiledat[[i]]          -->
<!--   tt <- table(dd$Contact) -->

<!--   if (length(tt)>0) { -->
<!--   for (ii in 1:length(tt)) -->
<!--     { -->
<!--     res[cc, 1] <- i -->
<!--     res[cc,2] <- (substr(dd$Date[i], 1,10)) -->
<!--     res[cc,3] <- nrow(dd) -->
<!--     res[cc,4] <- names(tt)[ii] -->
<!--     res[cc,5] <- tt[ii] -->
<!--     cc <- cc+1 -->
<!--     } -->
<!--   } -->
<!-- } -->


<!-- res <- res[!res$contact=="Investigation information",] -->
<!-- res <- res[!res$contact=="Investigation location",] -->
<!-- res$contact <- factor(res$contact, levels=c("Close", "Casual","Monitor")) -->


<!-- res <- res[order(res$contact),] -->
<!-- cols <- c( "red", "yellow","blue")[as.numeric(res$contact)] -->

<!-- ggplot(res, aes(x=Date,y=nsites))+geom_bar(stat="identity", position = "stack", width=1, aes(fill=contact))+ -->
<!--   xlab("update #")+ -->
<!--   ylab("# exposure sites")+ -->
<!--   ggtitle("`New` Exposure sites over updates") -->

<!-- ``` -->

## "New" Exposure sites for September (Gungahlin)

```{r echo = FALSE, message = FALSE, warning = FALSE}
#########function 1 ####################
fileFiles_function <- function(filesiwant){
  allfiles <- list.files(filesiwant, pattern=c("table_", ".csv"), full.names = TRUE)
  return(allfiles)
}
# Exposure sites per Update for august amd sept
filesiwant <- c("../data/allfiles/August/", "../data/allfiles/September/")

allfiles <- fileFiles_function(filesiwant = filesiwant)



############function 2 ######################
##function to link all files into a list[[i]]
countsperupdate <- function(allfiles){
  
  allfiledat <- list() #<- list() MUST BE OUTSIDE

    for(i in 1:length(allfiles)) {
      tib <- read_csv(allfiles[i]) %>%
            dplyr::select(Contact, Date, Suburb, Status) %>%
              filter(Suburb == "Gungahlin")
      #Status == "New" & 
    allfiledat[[i]] <- as.data.frame(tib)
  } #end loop
  
  return(allfiledat)
  
} #end function

##setup list of data
allfiledat <- list()
#run function
allfiledat <- countsperupdate(allfiles = allfiles)

res <- data.frame(update=NA, date=NA,locations=NA, contact=NA,nsites=NA )
cc<-1         

for(i in 1:length(allfiles)){
  
  dd <- allfiledat[[i]]         
  tt <- table(dd$Contact)
  
  if (length(tt)>0) {
  for (ii in 1:length(tt))
    {
    res[cc, 1] <- i
    res[cc,2] <- (substr(dd$Date[i], 1,10))
    res[cc,3] <- nrow(dd)
    res[cc,4] <- names(tt)[ii]
    res[cc,5] <- tt[ii]
    cc <- cc+1
    }
  }
}
  

res <- res[!res$contact=="Investigation information",]
res <- res[!res$contact=="Investigation location",]
res$contact <- factor(res$contact, levels=c("Close", "Casual","Monitor"))


res <- res[order(res$contact),]
cols <- c( "red", "yellow","blue")[as.numeric(res$contact)]

ggplot(res, aes(x=update,y=nsites))+geom_bar(stat="identity", position = "stack", width=1, aes(fill=contact))+
  xlab("update #")+
  ylab("# exposure sites")+
  ggtitle("`New` Exposure sites over updates")

```



## Time is interesting

There are several aspects of this information that has been captures. To turn this into a meaningful figure I will need to understand how long the duration of contact times and levels looked like. To do this:

length of time: start and end time 

```{r}

```




