---
title: "About the project"
---

Column {data-width=400}
------------------------------------------------------------

```{r setupabout, include=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(rmdformats)

## Global options
# options(max.print="75")
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache = FALSE,
	cache.path = "docs/",
	# width=75,
	comment = NA,
	prompt = FALSE,
	tidy = TRUE
)
```

This website tracks COVID-19 data and mobility information for the ACT and Canberra using code and data developed in the open source community. This information is only a guide. Please refer to official reports and press releases from government certified resources. <br>
- Government page: [ACT.govt.au](https://www.covid19.act.gov.au/)<br>
- Data: [ACT govt data](https://app.powerbi.com/view?r=eyJrIjoiZTY4NTI1NzQtYTBhYy00ZTY4LTk3NmQtYjBjNzdiOGMzZjM3IiwidCI6ImI0NmMxOTA4LTAzMzQtNDIzNi1iOTc4LTU4NWVlODhlNDE5OSJ9)<br>

```{r fig.align='center', fig.height=10, fig.width=8}
# ACT raw map
knitr::include_url("https://app.powerbi.com/view?r=eyJrIjoiZTY4NTI1NzQtYTBhYy00ZTY4LTk3NmQtYjBjNzdiOGMzZjM3IiwidCI6ImI0NmMxOTA4LTAzMzQtNDIzNi1iOTc4LTU4NWVlODhlNDE5OSJ9")

##html to data here


#save baseline

##check dayly


#interactive map in the future
```

#### ACT vaccine rollout

BRAND NEW and amazing app :) all abc top notch journalism (reproducible and transparent)

```{r fig.height=4, fig.width=8}
knitr::include_url("https://markusmannheim.github.io/act-coronavirus-teaser/")
```

#### Join mail list

<iframe src="https://docs.google.com/forms/d/e/1FAIpQLSdw-QWPpUsD6eH59kFJC5zJCXD6bExu7lmLboKdixR6iXJhAg/viewform?embedded=true" width="640" height="931" frameborder="0" marginheight="0" marginwidth="0">Loading…</iframe>
