---
title: "Covid19 case locations"
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               cache.path = "docs/")
```

<!-- This data is collected using code that accesses twitter, act govt site, nsw govt site, vic govt site...? -->

<sup>Disclaimer: This work This map shows the covid exposure locations in the ACT and is an **unofficial website** based on [official sources](https://www.covid19.act.gov.au/act-status-and-response/act-covid-19-exposure-locations). So if in doubt, refer to the [offical website](https://www.covid19.act.gov.au/act-status-and-response/act-covid-19-exposure-locations), which has now also an [**official map**](https://www.covid19.act.gov.au/act-status-and-response/act-covid-19-exposure-locations/map#Map-of-ACT-exposure-locations) included. Supported by Volunteers from the University of Canberra. Contacts: Bernd Gruber [bernd.gruber@canberra.edu.au] & Anthony Davidson [anthony.davidson@canberra.edu.au]</sup>

```{r eval = TRUE}
# source("R/plotly_source_script.R")
source("R/plotly_source_script.R")
```


### Map of Exposure sites

```{r}
# source("R/plotly_source_script.R")
library(plotly)
library(ggplotlyExtra)
library(leaflet)

leaflet(plotsumms) %>% addTiles() %>%
  addCircleMarkers(lat=plotsumms$lat,
                            lng=plotsumms$lon,
                   weight = 0.2, 
    radius = log(plotsumms$contactcount)*20,
                            popup = paste0(" COUNT:", plotsumms$contactcount),
                            fillOpacity = 0.1,
    # color = plotsumms$colsN,
   color = "grey50"
                            ) %>%
  addCircles(lat=tab4$lat,lng=tab4$lon,
             popup = paste0(plotsumms$Exposure.Location," ", plotsumms$Date), 
                            color = plotsumms$colsN,
                            stroke = TRUE,
                            fill = rep("black", length(plotsumms$colsN))) %>%
  addLegend("bottomright", 
            labels = levels(plotsumms$Contact), 
            colors = levels(plotsumms$colsN), 
            opacity = 0.8)
```

This website tracks COVID-19 data and mobility information for the ACT and Canberra using code and data developed in the open source community. This information is only a guide. Please refer to official reports and press releases from government certified resources.


## Data sources

[coming]