---
title: ""
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---


```{r setup, include=FALSE}
>>>>>>> dfdc6a2 (all mucked up)
title: "unoffical-ACT covid19 resources"
title: ""
>>>>>>> 168f783 (all mucked up)
date: "`r Sys.Date()`"
author:  "[Anthony Davidson](https://github.com/davan690)"
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```
# options(max.print="75")
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache = FALSE,
	cache.path = "docs/",
	# width=75,
	comment = NA,
	prompt = FALSE,
	tidy = TRUE
)
```

<!-- This data is collected using code that accesses twitter, act govt site, nsw govt site, vic govt site...? -->

<sup>Disclaimer: This work This map shows the covid exposure locations in the ACT and is an **unofficial website** based on [official sources](https://www.covid19.act.gov.au/act-status-and-response/act-covid-19-exposure-locations). So if in doubt, refer to the [offical website](https://www.covid19.act.gov.au/act-status-and-response/act-covid-19-exposure-locations), which has now also an [**official map**](https://www.covid19.act.gov.au/act-status-and-response/act-covid-19-exposure-locations/map#Map-of-ACT-exposure-locations) included. Supported by Volunteers from the University of Canberra. Contacts: Bernd Gruber [bernd.gruber@canberra.edu.au] & Anthony Davidson [anthony.davidson@canberra.edu.au]</sup>

```{r eval = FALSE, include=TRUE}
library(tidyverse)
library(ggmap)
library(leaflet)
library(plotly)
library(flexdashboard)
library(DT)
#latest dataset
tab3 <- read_csv("https://raw.githubusercontent.com/ACT-covid-resources/covid_canberra/main/data/last.csv")
# str(tab3)
# Aggregate method

cols <- c( "yellow", "red","cyan", "blue")

cc <- as.numeric(factor(tab3$Contact))

labs <- paste(tab3$Contact, tab3$Status,tab3$Exposure.Location, tab3$Street, tab3$Suburb, tab3$Date,tab3$Arrival.Time, tab3$Departure.Time, tab3$doubles, sep="<br/>") 

##plot the map


m <- leaflet() %>% addTiles()

m <- m %>% addCircleMarkers(lat=tab3$lat, lng=tab3$lon,popup = labs, weight=0.5, color = cols[cc], radius = 5 , fillOpacity = 0.8) 
m <- m %>% addLegend("bottomright", labels = levels(factor(tab3$Contact)), colors = cols, opacity = 1)
```

<!-- # ```{r title, results='asis'}  -->
<!-- #  -->
<!-- # cat(paste0("# ", params$lup)) -->
<!-- #  -->
<!-- # ``` -->

```{r include  = FALSE}
library(lubridate)
library(tidyverse)
library(plotly)
tab3 <- read_csv("https://raw.githubusercontent.com/ACT-covid-resources/covid_canberra/main/data/last.csv")
str(tab3)
#latest dataset
# tab3 <- ltab

# ## restructure data to look nice
# # tab3 %>%
# #   rename(`Place name` = Place)
# # Aggregate method
# labs <- paste(tab3$Place, tab3$Date,tab3$Arrival.Time, tab3$Departure.Time, sep="<br/>") 
# # names(tab3)
# datyl <-factor(tab3$Contact)
# # levels(datyl)
# 
# datyl1 <- tab3 %>%
#            filter(Status >= "New")

# names(tab3)
# colsN <- cols[datyl1]

tab4 <- tab3 %>%
  mutate(colsN = factor(Contact, levels = c("Close", "Casual", "Monitor","Investigation location")),
         Contact = factor(Contact, levels = c("Close", "Casual","Monitor", "Investigation location")))


levels(tab4$colsN) <- c("purple", "red","orange",  "grey50")
levels(tab4$colsN) <- c("red", "yellow","blue",  "teal")
# table(tab4$colsN)

# names(tab4)
tab4 %>%
  mutate(conDate = as.Date(lubridate::dmy(Date)),
         locName = as.factor(Exposure.Location))


##loc summaries
tab5 <- tab4 %>%
  mutate(conDate = as.Date(lubridate::dmy(Date)),
         locName = factor(Suburb)) %>%
  mutate(datNum = lubridate::day(conDate),
         weekname = lubridate::week(conDate))

glimpse(tab5)

Encoding(x = tab5$Exposure.Location) <- "UTF-8"
# ?Encoding
# replace all non UTF-8 character strings with an empty space
tab5$Exposure.Location <-
  iconv( x = tab5$Exposure.Location
         , from = "UTF-8"
         , to = "UTF-8"
         , sub = "" )

Encoding(x = tab5$Suburb) <- "UTF-8"
# ?Encoding
# replace all non UTF-8 character strings with an empty space
tab5$Suburb <-
  iconv( x = tab5$Suburb
         , from = "UTF-8"
         , to = "UTF-8"
         , sub = "" )

filter(tab5, Suburb == "Amaroo")$Suburb

str(tab5$Suburb)


##by suburb
sum1 <- tab5 %>%
  dplyr::group_by(Suburb, Status, Contact) %>%
    dplyr::summarise(casecount = length(unique(Date)),
                     time = conDate) %>%
    ungroup()



a <- as.data.frame(table(tab5$locName))

colnames(a) <- c("locName", "contactcount")

# head(a)
# str(a)
# filter(a, contactcount >=1)

plotsumms <- right_join(tab5, a)

print(a)
str(a)

# Aggregate method
# labs <- paste(plotsumms$Exposure.Location, plotsumms$Date,plotsumms$Arrival.Time, plotsumms$Departure.Time, sep="<br/>") 

# nrow(tab4)
#> [1] 100
# nrow(distinct(plotsumms, Suburb))
b <- distinct(plotsumms, Suburb, .keep_all = TRUE)
# subsTable <- semi_join(tab4, b)


#> [1] 69
# nrow(distinct(df, x, y))
# #> [1] 69
# levels(plotsumms$locName)
# distinct(df, x)
plotsumms <- b
plotsumms$Suburb[35] <- "O'Connor" 
plotsumms$locName[35] <- "O'Connor"
# plotsumms$Suburb <- droplevels(plotsumms$Suburb)
plotsumms$locName <- droplevels(plotsumms$locName)

clean <- plotsumms$Exposure.Location[4] <- "Assembly The People Pub"

# pre-processing
# ensure that all characters in the `Name` column
# are valid UTF-8 encoded
# Thank you to SO for this gem 
# https://stackoverflow.com/questions/17291287/how-to-identify-delete-non-utf-8-characters-in-r
Encoding(x = plotsumms$Exposure.Location) <- "UTF-8"
# ?Encoding
# replace all non UTF-8 character strings with an empty space
plotsumms$Exposure.Location <-
  iconv( x = plotsumms$Exposure.Location
         , from = "UTF-8"
         , to = "UTF-8"
         , sub = "" )


labs <- paste(plotsumms$Exposure.Location, plotsumms$Date,plotsumms$Arrival.Time, plotsumms$Departure.Time, sep="<br/>") 



# %>%
#     group_by(locName) %>%
#       summarise(countPlace = count(Place))
# # %>%
#   group_by(Suburb) %>%
#     summarise(FirstCase = min(conDate),
#               LastCase = max(conDate),
#               caseCount = sum(unique(Place)))

# write.csv(x = plotsumms, "data/outSubs.csv")
```
### Map of Exposure sites

```{r}
library(plotly)
library(ggplotlyExtra)
library(leaflet)

leaflet(plotsumms) %>% addTiles() %>%
  addCircleMarkers(lat=plotsumms$lat,
                            lng=plotsumms$lon,
                   weight = 0.2, 
    radius = log(plotsumms$contactcount)*5,
                            popup = paste0(" COUNT:", plotsumms$contactcount),
                            fillOpacity = 0.3,
    color = "grey50"
                            ) %>%
  addCircles(lat=tab4$lat,lng=tab4$lon,
             popup = paste0(plotsumms$Exposure.Location," ", plotsumms$Date), 
                            color = plotsumms$colsN,
                            stroke = TRUE,
                            fill = rep("black", length(plotsumms$colsN)))

```

This website tracks COVID-19 data and mobility information for the ACT and Canberra using code and data developed in the open source community. This information is only a guide. Please refer to official reports and press releases from government certified resources.

### Data sources

[coming]